\begin{acknowledge}
I would like to express my gratitude to several individuals and organizations
whose support was crucial to the completion of this research.

Foremost, I am indebted to my academic supervisor, Prof. Dr. Takayuki Ishizaki,
for his invaluable guidance and for welcoming me into his laboratory. His
mentorship was pivotal from the outset of this research, through times when I
was navigating unfamiliar territory. His insights have not only shaped this
study but have also deepened my interest and knowledge in the field of power
systems.

I extend my sincere thanks to Mr. Taku Nishino, a senior PhD candidate, whose
assistance was fundamental in my understanding of both the theoretical and
practical aspects of power systems simulation and analysis. His patience,
willingness to help, and engagement with my work were instrumental in overcoming
the challenges I encountered during this research.

This master's program also afforded me a cherished opportunity to connect with
my Japanese heritage, enhancing my understanding of Japan's culture and
language. This personal growth alongside my academic pursuits has been immensely
fulfilling.

I am grateful to my friends Petar Mircheski and Alex Stafie for the enriching
discussions that spanned a wide array of topics. Our conversations and shared
moments of camaraderie, particularly our regular coffee breaks, were a source of
encouragement throughout this journey.

Lastly, I wish to acknowledge the financial support provided by the Ministry of
Education, Culture, Sports, Science and Technology (MEXT) of Japan. This support
was essential in enabling me to pursue my Master's degree.

My heartfelt thanks go to all who have contributed to this research, directly or
indirectly. Your support has been invaluable.
\end{acknowledge}